Efficient ancestry and mutation simulation with msprime 1.0

### 2021-08-10 paper.tex

% Middle Authors
\author[8]{Bjarki Eldon}
\author[9]{Castedo E. Ellerman}
\author[10]{Jared G. Galloway}
\author[11]{Ariella L. Gladstein}
\author[12]{Gregor Gorjanc}
\author[13]{Guo, Bing}
\author[7]{Ben Jeffery}
\author[14]{Warren W. Kretzschmar}
\author[15]{Ivan Krukov}
\author[2]{Konrad Lohse}
\author[16]{Michael Matschiner}
\author[15]{Dominic Nelson}
\author[17]{Nathaniel Pope}
\author[18]{Consuelo D. Quinto-Cort\'es}
\author[10]{Murillo F. Rodrigues}
\author[19]{Kumar Suanack}
\author[20]{Thibaut Sellinger}
\author[21]{Kevin Thornton}
\author[22]{Hugo van Kemenade}
\author[7]{Anthony W. Wohns}
\author[7]{H. Yan Wong}

% Senior Authors
\author[15,$\dagger$]{Simon Gravel}
\author[10,$\dagger$]{Andrew D. Kern}
\author[23,$\dagger$]{Jere Koskela}
\author[10,24,$\dagger$]{Peter L. Ralph}

@@

% Bjarki
\affil[8]{Leibniz Institute for Evolution and Biodiversity
Science, Museum f\"ur Naturkunde Berlin }
% Castedo
\affil[9]{FIXME: CASTEDO's AFFILIATION}
% Jared, Murillo, Peter, Andy
\affil[10]{Institute of Ecology and Evolution, Department of Biology,
    University of Oregon}
% Ariella
\affil[11]{Department of Genetics, University of North Carolina at Chapel Hill}
% Gregor
\affil[12]{The Roslin Institute and Royal (Dick) School of Veterinary Studies,
    University of Edinburgh}
% Bing
\affil[13]{FIXME: BING's AFFILIATION}
% Winni
\affil[14]{FIXME: WINNI's AFFILIATION}
% Simon, Dom, Ivan
\affil[15]{Department of Human Genetics, McGill University}
% Michael
\affil[16]{FIXME: MICHAEL's AFFILIATION}
% Nathaniel
\affil[17]{FIXME: NATHANIEL's AFFILIATION}
% Consuelo
\affil[18]{National Laboratory of Genomics for Biodiversity (LANGEBIO),
    Unit of Advanced Genomics, CINVESTAV, Irapuato, Mexico}
% Saunack
\affil[19]{FIXME: SAUNACK's AFFILIATION}
% Thibaut
\affil[20]{Professorship for Population Genetics, Department of Life Science Systems, Technical University of Munich}
% Kevin
\affil[21]{Ecology and Evolutionary Biology, University of California at Irvine}
% Hugo
\affil[22]{FIXME HUGO's AFFILIATION}
% Jere
\affil[23]{Department of Statistics, University of Warwick}
% Peter (second affil)
\affil[24]{Department of Mathematics, University of Oregon}

>>>>

% Middle Authors
\author[8]{Bjarki Eldon}
\author[9]{Castedo E. Ellerman}
\author[10]{Jared G. Galloway}
\author[11,12]{Ariella L. Gladstein}
\author[13]{Gregor Gorjanc}
\author[14]{Guo, Bing}
\author[7]{Ben Jeffery}
\author[15]{Warren W. Kretzschmar}
\author[16]{Ivan Krukov}
\author[2]{Konrad Lohse}
\author[17]{Michael Matschiner}
\author[16]{Dominic Nelson}
\author[18]{Nathaniel S. Pope}
\author[19]{Consuelo D. Quinto-Cort\'es}
\author[10]{Murillo F. Rodrigues}
\author[20]{Kumar Suanack}
\author[21]{Thibaut Sellinger}
\author[22]{Kevin Thornton}
\author[23]{Hugo van Kemenade}
\author[7]{Anthony W. Wohns}
\author[7]{H. Yan Wong}

% Senior Authors
\author[15,$\dagger$]{Simon Gravel}
\author[10,$\dagger$]{Andrew D. Kern}
\author[24,$\dagger$]{Jere Koskela}
\author[10,25,$\dagger$]{Peter L. Ralph}

@@

% Bjarki
\affil[8]{Leibniz Institute for Evolution and Biodiversity
Science, Museum f\"ur Naturkunde Berlin }
% Castedo
\affil[9]{FIXME: CASTEDO's AFFILIATION}
% Jared, Murillo, Peter, Andy
\affil[10]{Institute of Ecology and Evolution, Department of Biology,
    University of Oregon}
% Ariella
\affil[11]{Department of Genetics, University of North Carolina at Chapel Hill}
\affil[12]{Embark Veterinary, Inc., Boston}
% Gregor
\affil[13]{The Roslin Institute and Royal (Dick) School of Veterinary Studies,
    University of Edinburgh}
% Bing
\affil[14]{FIXME: BING's AFFILIATION}
% Winni
\affil[15]{FIXME: WINNI's AFFILIATION}
% Simon, Dom, Ivan
\affil[16]{Department of Human Genetics, McGill University}
% Michael
\affil[17]{Natural History Museum, University of Oslo}
% Nathaniel
\affil[18]{Department of Entomology, Pennsylvania State University}
% Consuelo
\affil[19]{National Laboratory of Genomics for Biodiversity (LANGEBIO),
    Unit of Advanced Genomics, CINVESTAV, Irapuato, Mexico}
% Saunack
\affil[20]{FIXME: SAUNACK's AFFILIATION}
% Thibaut
\affil[21]{Professorship for Population Genetics, Department of Life Science Systems, Technical University of Munich}
% Kevin
\affil[22]{Ecology and Evolutionary Biology, University of California Irvine}
% Hugo
\affil[23]{FIXME HUGO's AFFILIATION}
% Jere
\affil[24]{Department of Statistics, University of Warwick}
% Peter (second affil)
\affil[25]{Department of Mathematics, University of Oregon}
